Regularising Lotka--Volterra Interaction Matrices by Species Grouping

### 2021-10-24 article.rnw
Add a quick and dirty AIC histogram.

The $R^2$ values of the models ranged from \rsquarednum{\Sexpr{min(brute_data$statistics$R2)}} to \rsquarednum{\Sexpr{max(brute_data$statistics$R2)}}.
The AIC values ranged from \aicnum{\Sexpr{min(brute_data$statistics$aic)}} to \aicnum{\Sexpr{max(brute_data$statistics$aic)}}.
\Cref{fig:aic} shows the distribution of AIC values from the models, with some models of interest marked.
%TODO: The AIC histogram.

>>>>

The $R^2$ values of the models ranged from \rsquarednum{\Sexpr{min(brute_data$statistics$R2)}} to \rsquarednum{\Sexpr{max(brute_data$statistics$R2)}}.
The AIC values ranged from \aicnum{\Sexpr{min(brute_data$statistics$aic)}} to \aicnum{\Sexpr{max(brute_data$statistics$aic)}}.
\Cref{fig:aic} shows the distribution of AIC values from the models, with some models of interest marked.

\begin{figure}
	<<echo=FALSE>>=
		hist(brute_data$statistics$aic,
			main="",
			xlab="AIC",
			xaxs='i',
			yaxs='i'
		)
		abline(v = brute_data$fully_separated_statistics$aic, lwd=2, lty="dashed", col="green")
		abline(v = brute_data$fully_grouped_statistics$aic, lwd=2, lty="dashed", col="red")
	@

	\caption{%
		A histogram of the AIC values of species interaction models with all possible groupings of interaction coefficients.
		The green line shows the AIC value (\aicnum{\Sexpr{brute_data$fully_separated_statistics$aic}}) of the ungrouped model, in which all competition coefficients are fitted independently.
		The red line shows the AIC value (\aicnum{\Sexpr{brute_data$fully_grouped_statistics$aic}}) of the full grouped model, where every pair os species shares a single interaction coefficient.
	}
	\label{fig:aic}
\end{figure}

\subsection{Coclassification of species}
